No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-07 R/MSE manuscript.Rmd
Fix alternative data join; fix string split for part.date_pub

alt.data_pub<-left_join(data_pub.join,mgmt,by=c("ID"="fkStudyID"))%>%
  select(-c("ID","ID.y"))
alt.data_CC<-left_join(data_CC.join,mgmt,by=c("ID"="fkStudyID"))%>%
  select(-c("ID","ID.y"))

@@

part.data_pub<- part.data_pub %>%
    purrr::map(~ strsplit(as.character(.),split=",")) %>%
    purrr::map(unlist) %>%
    purrr::map(table)

@@

part.data_CC<- part.data_CC %>%
  purrr::map(~ strsplit(as.character(.),split=",")) %>%
  purrr::map(unlist) %>%
  purrr::map(table)

>>>>

alt.data_pub<-left_join(data_pub.join,mgmt.join,by=c("ID"="fkStudyID"))%>%
  select(-c("ID"))
alt.data_CC<-left_join(data_CC.join,mgmt.join,by=c("ID"="fkStudyID"))%>%
  select(-c("ID"))

@@

part.data_pub<- part.data_pub %>%
    purrr::map(~ strsplit(as.character(.),split=", ")) %>%
    purrr::map(unlist) %>%
    purrr::map(table)

@@

part.data_CC<- part.data_CC %>%
  purrr::map(~ strsplit(as.character(.),split=", ")) %>%
  purrr::map(unlist) %>%
  purrr::map(table)
